Assessing glymphatic transport velocities by adjoint methods

### 2018-10-19 tex/paper.tex
update with natbib, citet not working properly, do not know why

\documentclass[11pt,a4paper]{article}
\usepackage{hyperref}
\usepackage{color}
\usepackage{amsmath, amsthm, amssymb, amsfonts, verbatim}
\usepackage{graphicx}
\usepackage[table,x11names]{xcolor}
\usepackage{geometry}
\usepackage{subcaption}

@@

\begin{abstract}
bla bla 
\end{abstract}
\section{Introduction}
Recent breakthroughs in medicine have linked diseases like Alzheimer's to insufficient sleep through a novel biomechanical mechanism called the glymphatic system 
that is responsible for waste clearance. 
In 2011,~\cite{iliff2012paravascular} discovered a novel system within our brain's metabolism system, which changed our understanding of the brain. 
The system involves a new pathway, called the paravascular pathway as it runs in parallel with vasculature system in a surrounding compartment.
The important novelty in the 2011 findings was that waste from the brain is cleared through the paravascular path, and that a malfunction of this system 
is linked to the development of dementia such as Alzheimer's and Parkinson's diseases. In 2013,~\cite{xie2013sleep} found
that this system is particularly active during sleep.
These mentioned breakthroughs were all performed in mice. In 2018,  
the project's collaborators for the first time demonstrated the action of
this system in humans, and that the action of the system differs
between healthy controls and patients with dementia~\cite{ringstad2018brain}. 
However, the biomechanical mechanisms behind this is not well understood,
and so far the modeling attempts have mostly failed~\cite{asgari2016glymphatic, holter2017interstitial, smith2017glymphatic}. 
In particular the system seems to facilitate waste transport faster than  
the diffusion, which since the pioneering works of \cite{sykova2008diffusion} 
has been the prevailing paradigm. Here, we aim to investigate whether PDE constrained optimization can be used
to assess the effective diffusion coefficient on long time-scales (hours or days).

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage{hyperref}
\usepackage{color}
\usepackage{amsmath, amsthm, amssymb, amsfonts, verbatim}
\usepackage{graphicx}
\usepackage[table,x11names]{xcolor}
\usepackage{geometry}
\usepackage{subcaption}
\usepackage[numbers]{natbib}

@@

\begin{abstract}
bla bla 
\end{abstract}
\section{Introduction}
Recent breakthroughs in medicine have linked diseases like Alzheimer's to insufficient sleep through a novel biomechanical mechanism called the glymphatic system 
that is responsible for waste clearance. 
In 2011,~\citet{iliff2012paravascular} discovered a novel system within our brain's metabolism system, which changed our understanding of the brain. 
The system involves a new pathway, called the paravascular pathway as it runs in parallel with vasculature system in a surrounding compartment.
The important novelty in the 2011 findings was that waste from the brain is cleared through the paravascular path, and that a malfunction of this system 
is linked to the development of dementia such as Alzheimer's and Parkinson's diseases. In 2013,~\citet{xie2013sleep} found
that this system is particularly active during sleep.
These mentioned breakthroughs were all performed in mice. In 2018,  
the project's collaborators for the first time demonstrated the action of
this system in humans, and that the action of the system differs
between healthy controls and patients with dementia~\cite{ringstad2018brain}. 
However, the biomechanical mechanisms behind this is not well understood,
and so far the modeling attempts have mostly failed~\cite{asgari2016glymphatic, holter2017interstitial, smith2017glymphatic}. 
In particular the system seems to facilitate waste transport faster than  
the diffusion, which since the pioneering works of \cite{sykova2008diffusion} 
has been the prevailing paradigm. Here, we aim to investigate whether PDE constrained optimization can be used
to assess the effective diffusion coefficient on long time-scales (hours or days).
